### 2019-10-11 thesis/txt/2-models.tex
wrting about tool impl and data set data points

@@

\section{Our Model for Information Extraction Techniques}
\begin{figure}[h]
	\centering
	\includegraphics[page=3, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
	\caption{Model for an information extraction technique}
	\label{fig:model-ie-technique}
\end{figure}
\plan{model = making a picture with boxes to visualize what we are talking about}
A build log information extraction technique (BLIE technique) consumes a build log (text file) and produces a certain output (text). \todo{make picture, output can be contained in log or not, can be continuous substring or selected lines etc.}.
\begin{itemize}
	\item{Target}{Extractable Information} each extraction technique \todo{instantiation!} targets a specific information
	\item{Setup Overhead}{Time}
	\item{Performance}{Performance} split into learning performance
\end{itemize}

>>>>

\plan{a build consists of various steps, executed by different tools, these are often orchestrated by at least one overarching tool. // picture: overarching tool travis and it calls different tools which tehn output sequentiall, travis sometimes outputs something in between -> that is how the build log is made up // we have this structure though it is not always apparent from the build log / edges between the systems can look very different, mostly no agreed model, we: look at differen techniques to extract certain pieces of information \emh{without complete parsing the whole log in to a structure} -> we don't necesarrily want to understand the whole log sturcture just extract one specifi information relevant to us}

@@

\section{Our Model for Information Extraction Techniques}
\begin{figure}[h]
	\centering
	\includegraphics[page=3, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
	\caption{Model for an information extraction technique}
	\label{fig:model-ie-technique}
\end{figure}
\plan{model = making a picture with boxes to visualize what we are talking about}
A build log information extraction technique (BLIE technique) consumes a build log (text file) and produces a certain output (text). \todo{make picture, output can be contained in log or not, can be continuous substring or selected lines etc.}.
\begin{itemize}
	\item{Target}{Extractable Information} each extraction technique \todo{instantiation!} targets a specific information
	\item{Setup Overhead}{Time}
	\item{Performance}{Performance} split into learning performance
	\item \textbf{Configuration Scope} for one repository/project, a language/logkind, global
\end{itemize}

### 2019-10-11 thesis/txt/3-data-set.tex
wrting about tool impl and data set data points

\section{Labeling}
For our study, described in Chapter \ref{sec:study}, we want to investigate the extraction capabilities of three techniques. Therefore, we need a data set of in/output examples for one \texttt{BuildLogInformation}. Furthermore, Keyword search is not configured by such in/output, but search keywords surrounding the desired output. Finally, this section describes our notion of structural categories, which we use to quantify our assumptions on the needed uniformness of in/output examples.

  \subsection{Build Failure Reason}

    \paragraph{Description}
    WHY? one common information developers and researches might want to extract, intentionally not focus on one structurally clearly defined extraction   cause that would be simple for PROSE extraction -> better comparability
    \paragraph{Labeling Process}

  \subsection{Keywords}

    \paragraph{Description}
    for simple keyword search - imitate what users would search for ad-hoc

    learning steps combining keywords -> similar to how devs would learn from reading those models

    \paragraph{Labeling Process}

  \subsection{Categories}

    \paragraph{Description}

    \paragraph{Labeling Process}

\section{Validation}
\todo{copy over from md doc}

>>>>

\section{Build Failure Reason}
\todo{WHY? one common information developers and researches might want to extract, intentionally not focus on one structurally clearly defined extraction   cause that would be simple for PROSE extraction -> better comparability}

\section{Data Model}
For our study, described in Chapter \ref{sec:study}, we want to investigate the extraction capabilities of three techniques. Therefore, we need a data set of in/output examples for one \texttt{BuildLogInformation}. Furthermore, Keyword search is not configured by such in/output, but search keywords surrounding the desired output. Finally, this section describes our notion of structural categories, which we use to quantify our assumptions on the needed uniformness of in/output examples.

\subsection{Example Set}
Our data set is organized in example sets. One example set always contains build log in/output examples from the same software repository or project and for one specific build log information. They are all from one repository because we investigate information extraction techniques which are always configured to the scope of one particular software repository or project.
Each example set has an identifying \emph{save name}, a \emph{build log information} that is desired to be extracted by this configuration, and a list of \emph{in / output examples}.

\subsection{In / Output Example}
In/output examples (I/O examples) are used to configure two of the information extraction techniques we are evaluating for this thesis, PROSE regular expression program synthesis by example and text similarity. In our data set they always consist of an \emph{input path}, linking to the build log file which is the input for this example. The \emph{output} is a substring of that build log, the textual representation of the targeted build log information within the input build log.

\subsection{Keywords}
The keyword search is configured by a list of keywords which are searched in the document with plain text search. In order to compare it to the two other techniques, each in/output example is associated with a list of 1 - 3 keywords that can be found close to the textual representation of the targeted build log information.

\paragraph{Description}
\todo{for simple keyword search - imitate what users would search for ad-hoc}

\todo{learning steps combining keywords -> similar to how devs would learn from reading those models}

\subsection{Categories}
Our intuition was that the ability of PROSE to be able to successfully learn a regex program depended on the structural uniformity of the provided in/output examples.
The regular expressions need a consistent pattern in the build log string at the borders or around the textual representation of a build log information to match on for the extraction.
To be able to quantify this intuition in our evaluation we assigned \emph{structural categories} to each of the examples within an example set.
If two extractions are at the same structural location with the build log, meaning they are surrounded by a similar markings, the fall into the same category.
For most cases, two build failure reason examples which fall into one category are outputted either within the same build step or by the same build step tool.

\section{Labeling}
\subsection{Output Examples: Build Failure Reason}
We labeled the first occuring substring describing the failure. If there were multiple errors described we took the first continuous block of error description.

The labeler read or skimmed through build log and copy out the substring describing the reason the build failed. Whitespace or special characters were preserved, as they might be crucial for an information extraction technique to detect the desired.
Because we are using xml to save our example sets, we also had to make sure to escape respective special characters (ampersand, less than).

\section{Validation}
We vaildated our collected labels in two different ways. We did a second pass of labeling the build failure reason, keywords and categoies on a subset of the data and compared the results to calculate the inter-rater reliability using cohens kappa. In addition, we sent out a survey to the developers, whose commits triggered the builds within our data set and asked them whether our extraction of the log part describing the reason the build failed was correct. In the following we describe the results of those two validation studies.

### 2019-10-11 thesis/txt/4-tool.tex
wrting about tool impl and data set data points

\chapter{Our Information Extraction Tool}
\label{sec:implementation}
describe implemantation of Tool
\begin{figure}[h]
	\centering
	\includegraphics[page=7, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
	\caption{Our tool unifying different information extraction techniques for build logs}
	\label{fig:tool}
\end{figure}

@@

Common options:
    -h, --help                       Show this message
\end{lstlisting}
unification tool, reference CLI somehow nicely?,

@@

\section{PROSE Program Synthesis}
implementation details :)

>>>>

\chapter{Our Information Extraction Tool}
\label{sec:implementation}
We implemented prototypes for our three focus information extraction techniques to evaluate them on our collected build logs.
This section will present our unified interface and describe the implementation of each of the techniques.

\begin{figure}[h]
	\centering
	\includegraphics[page=7, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
	\caption{Our tool unifying different information extraction techniques for build logs}
	\label{fig:tool}
\end{figure}

@@

Common options:
    -h, --help                       Show this message
\end{lstlisting}
As we implemented the information extraction techniques in different languages, choosing one that fits the respective technique each time, we decided to abstract over language differences for cli arguments by creating a unified interfaces. Our unified interface then in turn calls the various different IE techniques over the command line.

We provide two different modes: \emph{analysis} and \emph{evaluation}.
The \emph{analysis} takes a path to a file you want to analyze and all the configuration necessary for a specific technique and returns the resulting extraction on the console output. The \emph{evaluation} takes an

unification tool, reference CLI somehow nicely?,

@@

\section{PROSE Program Synthesis}
The first technique we implemented was the PROSE regular expression program synthesis. As it is based on the PROSE library from Microsoft provided in C\# we also chose C\# for our tool. 
implementation details :)
